Measuring Perceptions and Preferences for Meritocracy

### 2021-01-19 docs/paper.Rmd
... y update lista autores

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra & Francisco Meneses <br><br>"
abstract: "Economic and social inequalities have generated growing concern and crises across contemporary societies. One of the mechanisms proposed by the social sciences to explain the maintenance of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel, and as it is based upon multiple approaches and techniques, its interpretation can be difficult and confusing. Adding to these difficulties, is the fact that many such studies have relied upon secondary data to operationalize meritocracy, with significant variation in the use and interpretation of survey items. Based on a review of studies that measure meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding the conceptualization and indicators of meritocracy. Based on this critical analysis, we propose a scale named the *Perceptions and Preferences for Meritocracy Scale*, which we test with confirmatory factor analysis, using data from an online survey study (N=2,141). Our results support the proposed conceptual structure, which not only distinguishes between perceptions and preferences, but also between meritocratic and non-meritocratic dimensions. Our discussion highlights the importance of considering these different dimensions in order to advance the study of meritocracy."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
  - ../input/bib/invariance.bib
editor_options:
  chunk_output_type: console
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

>>>>

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra, Luis Maldonado, Francisco Meneses & Jorge Atria <br><br>"
abstract: "Economic and social inequalities have generated growing concern and crises across contemporary societies. One of the mechanisms proposed by the social sciences to explain the maintenance of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel, and as it is based upon multiple approaches and techniques, its interpretation can be difficult and confusing. Adding to these difficulties, is the fact that many such studies have relied upon secondary data to operationalize meritocracy, with significant variation in the use and interpretation of survey items. Based on a review of studies that measure meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding the conceptualization and indicators of meritocracy. Based on this critical analysis, we propose a scale named the *Perceptions and Preferences for Meritocracy Scale*, which we test with confirmatory factor analysis, using data from an online survey study (N=2,141). Our results support the proposed conceptual structure, which not only distinguishes between perceptions and preferences, but also between meritocratic and non-meritocratic dimensions. Our discussion highlights the importance of considering these different dimensions in order to advance the study of meritocracy."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
  - ../input/bib/invariance.bib
editor_options:
  chunk_output_type: console
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---
